Carbon cathodes for rechargeable aluminium-ion batteries

### 2019-12-27 manuscript.tex

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{upgreek}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tgtermes}
\usepackage{subfig}
\usepackage[version=4]{mhchem}
\usepackage{threeparttable}
\onehalfspacing
\graphicspath{figures/}
\usepackage{array, booktabs}
\setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{8pt}
\renewcommand{\arraystretch}{1.5}
\title{Carbon cathodes for rechargeable aluminium-ion batteries}
\author{
  Shalini Divya\\
  School of Chemical and Physial Sciences\\
  Victoria University of Wellington\\
  Wellington, New Zealand\\
  \texttt{shalini.divya@vuw.ac.nz}\\
  %% examples of more authors
   \And
  Thomas Nann\thanks{Corresponding author.}\\
  School of Mathematical and Chemical Sciences\\
  The University of Newcastle\\
  Newcastle, NSW 2308, Australia\\
  \texttt{thomas.nann@newcastle.edu.au}\\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
\maketitle
\begin{abstract}
 In this work, we compare four different forms of carbon: activated carbon from human hair, activated carbon from hemp fibers, a fullerene mixture consisting of \ce{C60} and \ce{C70} fullerenes (CFEx) and Super-P carbon black (SPCB) as cathodes for non-aqueous aluminium-ion batteries. These materials differ in their general structure, porosity and morphology. The fullerenes display a crystalline structure, whereas hemp fibers, Super-P and ACH are amorphous in nature. Of all materials, ACH recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$. Both hemp fibers and SPC achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively. CFEx recorded its highest capacity at 78 mAh g$^{-1}$ and maintained it for 50 cycles. The cells were charged and discharged to 2.45 V and 0.2 V respectively. 
 \end{abstract}

@@

\section{Introduction}
Different varieties of carbon-based materials have been widely used in energy storage applications. Graphite, with its layered structure turned out to be an ideal intercalation cathode material \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}. Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011}. Aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium. Thus, they offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}. In this work, we tested a number of rechargeable AIBs using an ionic liquid electrolyte with different carbon-based cathodes. The aim of this study was to systematically explore the properties of different carbon-materials when used as AIB cathodes.

Graphite has been commonly used as a cathode in AIBs. It has a layered structure that enhances the intercalation process, good conductivity, and a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V. Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$. The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge. X-ray diffraction (XRD) and Raman spectroscopy studies have widely been used to establish this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017, lin_ultrafast_2015} as shown in Figure \ref{SF:graphitemech}. Raman data showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation. XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{SF/graphitemech}
    \caption{Intercalation of \ce{AlCl4-} ions while cell charging and deintercalation during discharge in a Al/graphite cell. The interlayer distance between two graphite sheets is 3.3 \AA.}
  \label{SF:graphitemech}
\end{figure}

In this study, we compared four carbon-based materials with carbonised natural products. Super-P carbon has been used consistently as an additive to overcome conductivity loss in the active electrode material (for example, when a polymer binder such as polyvinylidene fluoride (PVDF) is added to it). Using it as an active material, we tried to find if Super-P contributes any capacity of its own to the battery's specific capacity. Activated carbon from natural products like rice or wood have been previously used in super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}. Also known as 'hierarchical porous carbons', these structures contained pores of various sizes (mesopores and micropores), which enhanced the charge storage capacity by increasing the surface area of the electrodes. The pores absorb the charge carriers reversibly on their surface. Based on this hypothesis, we used activated carbon from human hair and hemp fibers as cathodes.

@@

\begin{table}[tbh!]
\caption{Comparing average battery metrics of carbon cathodes} \label{table1}
\begin{center}
\begin{tabular}{|lcccc|}
\hline
Active material & {\textbf{Size}} & {\textbf{Specific capacity}} & {\textbf{Cell efficiency}} & {\textbf{Cell voltage}}\\
 & {\textbf{(pore size)}} & {\textbf{(mAh g$^{-1}$)}} & {\textbf{(\%)}} & {\textbf{(V)}}\\
\hline
Human hair & 5${\mu}$ m & 102 & 97 & 1.9 \\
Fullerene mix & 8.8 \AA & 78 & 85 & 1.7 \\
Hemp fibers & 2.3 $\mu$ m & 49 & 75 & 1.8 \\
SPCB & 300 \AA & 46 & 40 & 1.5 \\
\hline  % Please only put a hline at the end of the table
\end{tabular}
\end{center}
\end{table}

\begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/CDCall}
    \caption{Specific capacities in the a) 1$^{st}$ and b) 50$^{th}$ cycle of human hair, hemp fiber, CFEx and SPCB cathodes at a current rate of 50 mA g$^{-1}$. c) Cell efficiencies of cells at a current rate of 50 mAg$^{-1}$. d) Specific capacities of carbon cells at current rates of 25 mAg$^{-1}$, 50 mAg$^{-1}$ and 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al. }
  \label{figures:CDCall}
\end{figure}

Our battery system comprised a cathode, 99\% pure aluminium foil as an anode, and a room temperature ionic liquid (RTIL) acting as the electrolyte. ACH, hemp fibers and Super-P had an amorphous structure, however Raman spectra confirmed the presence of a few graphitic planes. Any number of graphite-like layers would allow \ce{AlCl4-} ions to intercalate when the cell was charged. However, CFEx, a mixture of \ce{C60} and \ce{C70} fullerenes, had crystalline character. Intercalation of aluminium into the fullerene cages was not observed. We suggest that \ce{AlCl4-} anions migrated through the gaps present in between fullerenes without altering the molecular structure. Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{figures:CDCall}a and b). Structural changes in the cathode before and after the cycles were studied using Raman spectra, XRD spectra and scanning electron microscopy (SEM) images.

Figure \ref{figures:CDCall}a and b compares the specific capacities of all cells recorded in their 1$^{st}$ and 50${^th}$ cycles. Cells made of human hair displayed the highest capacity at around 100 mAh g$^{-1}$ with a coulombic efficiency at $\sim$95$\%$. High surface area due to the porous structure of the materials might have led to a additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}. Hemp cells displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles. CFEx cells displayed a capacity of around 80 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\%. With an initial capacity of 84 mAh g$^{-1}$, specific capacity of SPCB cells decreased to 47 mAh g$^{-1}$ and a low coulombic efficiency at around 40\% was recorded. Capacity for SPCB and hemp cells decreased considerably after repeated charge/discharge cycles. A low coulombic efficiency (observed in both hemp and SPCB cells) can be attributed to parasitic reactions of the battery. These can include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes}. However, capacity fade for CFEx and human hair cells was minimal. This suggest that CFEx and human hair have a more stable structure compared to hemp and SPCB and they store charge reversibly \cite{pramanick}.

% In the above paragraph, you discuss 3 specific cells. This is suicidal (metaphorically speaking). In science you make a point by showing that something is reproducible. Having done just 3 expriments is asking for the reviewer to knock it down. You need to re-write this in a more general manner.

The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonized precursor. Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas}. Using alkali hydroxides, such as sodium and potassium hydroxide at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}. In this work, sodium hydroxide (NaOH) was used as the activating agent. The reaction that takes place inside the matrix after adding NaOH is:

\begin{center}
    4NaOH + C $\longrightarrow$ 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{satish}
\end{center}

NaOH was reduced to free metal, Na, these atoms in turn expanded the carbon matrix after intercalating into the carbon structure. Increased temperature ($\sim$900$^{\circ}$ C) forces the  atoms out of the carbon matrix, thus creating micropores. Oxidation of carbon from oxygen atoms of the hydroxide group forms \ce{CO2} providing routes for channeling the Na atoms into the internal structure leading to well-connected porous structure \cite{satish}. The calcinating temperature used here was 750$^{\circ}$ C. Figure \ref{SF:ACHsyn} displays the flowchart for activated carbon synthesis.

@@

% Above paragraph: Lots of unnecerssary information (see comments). Focus on what is relevant. Also sentences like the Carbon Valley one are suicidal. When you write, always have your worst scientific enemy in mind and write it so that you win.

Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals diameter of 11 \AA in a single crystal. However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}. They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}. To test their solubility in \ce{AlCl3}-EMImCl, 100 mg of CFEx was mixed in the electrolyte and stirred for 24 hours. The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box. CFEx seemed to dissolve in our electrolyte (Figure \ref{SF:CFExsol} since no phase separation was observed. It has been reported that poly-sulphides formed during cycling in a lithium-sulfur battery, are soluble in the electrolyte. They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}. Since no such effect was observed in aluminium-fullerene cells, this phenomena does not seem to impact the charge-storing capacity of CFEx. On the contrary, the cells displayed excellent capacity retention at various current rates(Figure \ref{figures:CDCall}d).

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/superPmech}
    \caption{Suggested mechanism for a \textbf{Al/Super-P} cell. Super-P has a very amorphous structure with a few graphite-like planes present in it. \ce{AlCl4-} ions intercalate into those layers and give the cell its capacity. However, cathode pulverisation results in capacity fading.}
  \label{figures:superPmech}
\end{figure}

Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure. Its pore size ranges from $\sim$30-50 nm \cite{younesi_analysis_2015}. SPCB has the least graphitic structure if compared to human hair and hemp fibers. It seems continuous cycling might have destroyed the arrangement of the carbon atoms, which resulted in poor capacity retention and low coulombic efficiencies.

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/hempmech}
    \caption{Suggested mechanism for a \textbf{Al/hemp} cell. The fibers have a large pore size (2.0-2.5 $\mu$m) which allow the \ce{AlCl4-} to get absorbed on the cathode surface but agglomeration of carbon atoms after a few cycles reduces the active sites available for charge storage, which reduces cell's capacity after every cycle.}
  \label{figures:hempmech}
\end{figure}

 \begin{figure}[tbh!]
  \centering
  \includegraphics[width=\textwidth]{figures/raman}
    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx , b) hemp fibers, c) ACH and d) Super-P cathodes indicating presence of both D and G-bands.}
  \label{figures:raman}
\end{figure}

In aluminum-graphite cells, it has been established that \ce{AlCl4-} ions intercalate while charging \cite{lin_ultrafast_2015}. Since the materials we tested have graphitic planes present, we focused our analysis on the pristine and charged electrodes. Figure \ref{figures:raman} displays Raman spectra of the tested cathodes. Pristine human hair, hemp fibers and SPCB had a significant D-band present indicating absence of an ordered structure with presence of lattice defects and deformities (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB). Figure \ref{figures:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules. The 'pentagonal pinch mode', which is usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$. However, \ce{C70} has multiple bands. Reduction in its molecular symmetry increases the number of vibrational modes, thus increasing the active Raman bands \cite{kimbrell_analysis_2014}. Pristine CFEx cathode was composed of both \ce{C60} and \ce{C70} Raman bands as seen in Figure \ref{figures:raman}c. It was interesting to note that charged CFEx cathodes looked strikingly similar. Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the structure remained intact after cycles. Human hair has a high surface area and an inter-connected mesoporosity. The charged cathodes showed a higher FWHM which suggests an increase in the lattice defects. Obviously, these defects arise after intercalation of chloroaluminates; it is assumed that these ions intercalate into the few graphitic planes present in the carbon matrix. In addition, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}. Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge\cite{brezesinski_ordered_2010}. A schematic of a possible mechanism is shown in Figure \ref{figures:ACHmech}.
%contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.  
Hemp fibers and SPCB had fewer graphitic planes and a highly disordered structure to begin with. The lattice defects seemed to increase after galvanostatic cycles. Continuous intercalation or absorption of ions on their surface would have further destroyed the cathode structure. This might be the reason why hemp and SPCB cells failed to retain capacity after a few cycles. However, CFEx does not have graphitic planes. It consists of a bunch of \ce{C60} and \ce{C70} fullerenes. Insertion of \ce{AlCl4-} ions inside the cage-like structure would be thermodynamically impossible. Since the fullerenes have a very high surface area, surface adsorption of ions is likely \cite{adams}. Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes \ref{figures:CFExmech}. Capacity retention of the aluminium-CFEx cells suggests that the interaction between the fullerenes and \ce{AlCl4-} ions takes place in a systematic way.

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{upgreek}
\usepackage{graphicx}
%\usepackage{setspace}
%\usepackage{tgtermes}
%\usepackage{subfig}
\usepackage[version=4]{mhchem}
\usepackage{threeparttable}
\usepackage{array, booktabs}
\setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{8pt}
\renewcommand{\arraystretch}{1.5}
\title{Carbon cathodes for rechargeable aluminium-ion batteries}
\author{
  Shalini Divya\\
  School of Chemical and Physial Sciences\\
  Victoria University of Wellington\\
  Wellington, New Zealand\\
  \texttt{shalini.divya@vuw.ac.nz}\\
  %% examples of more authors
   \And
  Thomas Nann\thanks{Corresponding author.}\\
  School of Mathematical and Chemical Sciences\\
  The University of Newcastle\\
  Newcastle, NSW 2308, Australia\\
  \texttt{thomas.nann@newcastle.edu.au}\\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
\maketitle
\begin{abstract}
 In this work, we compare four different forms of carbon: activated carbon from human hair, activated carbon from hemp fibers, a fullerene mixture consisting of \ce{C60} and \ce{C70} fullerenes (CFEx) and Super-P carbon black (SPCB) as cathodes for non-aqueous aluminium-ion batteries. These materials differ in their general structure, porosity and morphology. The fullerenes display a crystalline structure, whereas hemp fibers, SPCB and hair are amorphous in nature. Of all materials, activated carbon from human hair recorded the highest specific capacity after 50 cycles at 103 mAh g$^{-1}$ with a coulombic efficiency of $\sim$90\% at a current rate of 50 mV s$^{-1}$. Both hemp fibers and SPCB achieved their highest specific capacities at 56 mAh g-1 and 84 mAh g$^{-1}$ respectively. CFEx recorded its highest capacity at 78 mAh g$^{-1}$ and maintained it for 50 cycles. The cells were charged and discharged to 2.45 V and 0.2 V respectively. 
 \end{abstract}

@@

\section{Introduction}
Different varieties of carbon-based materials have been widely used in energy storage applications. Graphite, with its layered structure turned out to be an ideal intercalation cathode material \cite{ji_recent_2011, yoo_large_2008, lian_large_2010}. Activated carbon, owing to its porous structure, provides a high surface area for absorption of electrolyte ions in super-capacitors \cite{eliad_ion_2001, zhu_carbon-based_2011-2}. Non-aqueous aluminium-ion batteries (AIBs) use low-cost, abundant materials, a non-flammable electrolyte and provide a higher theoretical energy density than lithium-ion batteries (LIBs) due to the multivalent nature of aluminium. They offer an interesting potential long-term alternative to the problematic LIB technology \cite{ambroz_trends_2017-1}. In this work, we tested a number of rechargeable AIBs using an ionic liquid electrolyte with different carbon-based cathodes. The aim of this study was to systematically explore the properties of different carbon-materials when used as AIB cathodes.

Graphite has been repeatedly used as a cathode in AIBs. It has (i) a layered structure that enhances the intercalation process, (ii) good conductivity, and (iii) a high electrical potential {\it vs.} \ce{Al}/\ce{Al^3+} of 2.1 V. Various forms of graphite such as fluorinated graphite \cite{rani_fluorinated_2013}, kish graphite flakes \cite{wang_kish_2017}, three-dimensional (3D) graphitic-foam\cite{wu_3d_2016}, graphene aerogels\cite{huang_graphene_2019} and several other forms have been tested as cathodes for AIBs, showing typical specific capacities ranging from 60-250 mAh g$^{-1}$. The \ce{AlCl4-}-anions intercalate into the graphitic stacks when the cell is being charged and deintercalate during discharge. X-ray diffraction (XRD) and Raman spectroscopy studies helped in establishing this mechanism \cite{rani_fluorinated_2013, wang_advanced_2017,lin_ultrafast_2015-3} as shown in Figure \ref{fig:graphitemech}. For example: a Raman spectra showed conversion of a doublet peak during charge to one single peak after the cell was fully charged, indicating two stages of intercalation. XPS studies confirmed reversible oxidation/reduction of carbon when \ce{AlCl4-} anions intercalate/deintercalate respectively \cite{stadie_zeolite-templated_2017, liu_binder-free_2019,wei_amorphous_2017}.

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{fig/graphitemech}
    \caption{Intercalation of \ce{AlCl4-} ions during charging and deintercalation during discharging in an Al/graphite cell. The interlayer distance between two graphite sheets is 3.3 \AA.}
  \label{fig:graphitemech}
\end{figure}

In this study, we compared four carbon-based materials with carbonised natural products. Super-P has been the premium choice for a carbon additive, while preparing a slurry, as it improves the conductivity of the active material. Using it as an active material, we tried to find if Super-P adds any capacity of its own to the battery's specific capacity. Activated carbon from natural products like rice or wood have been previously used in super-capacitors \cite{hussain_development_2019, frackowiak_carbon_2001}. Also known as 'hierarchical porous carbons', these structures contain pores of various sizes (mesopores and micropores), which enhance the surface area of the electrodes. The pores absorb the charge carriers reversibly on their surface by faradaic/ non-faradaic processes. Based on this hypothesis, we tested activated carbon from human hair and hemp fibers as cathodes for non-aqueous AIBs.

@@

\begin{table}[h!]
\caption{Comparing battery metrics of all carbon-based cathodes tested in this work} \label{table1}
\begin{center}
\begin{tabular}{|lcccc|}
\hline
Active material & {\textbf{Size}} & {\textbf{Specific capacity}} & {\textbf{Cell efficiency}} & {\textbf{Cell voltage}}\\
 & {\textbf{(pore size)}} & {\textbf{(mAh g$^{-1}$)}} & {\textbf{(\%)}} & {\textbf{(V)}}\\
\hline
Human hair & 5${\mu}$ m & 102 & 97 & 1.9 \\
Fullerene mix & 8.8 \AA & 78 & 85 & 1.7 \\
Hemp fibers & 2.3 $\mu$ m & 49 & 75 & 1.8 \\
SPCB & 300 \AA & 46 & 40 & 1.5 \\
\hline  % Please only put a hline at the end of the table
\end{tabular}
\end{center}
\end{table}

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{fig/CDCall}
    \caption{Specific capacities of AC (human hair, hemp fibers), CFEX and SPCB in their a) first and b) 50$^{th}$ cycle at a current rate of 50 mA g$^{-1}$. c) Coulombic efficiencies of cells at a current rate of 50 mAg$^{-1}$. d) Galvanostatic charge/discharge profile of all cells at various current rates ranging from 25 mAg$^{-1}$ to 100 mAg$^{-1}$ in a two-electrode setup against Al$^{3+}$/Al.}
  \label{fig:CDCall}
\end{figure}

The battery system comprised a cathode, 99\% pure aluminium foil as the anode, and a room temperature ionic liquid (RTIL) as the electrolyte. Activated carbon derived from human hair and hemp fibers, and SPCB have a non-crystalline structure, however their Raman spectra revealed the presence of a few graphitic planes. Graphitic layers would allow \ce{AlCl4-} ions to intercalate during charging. CFEx (a mixture of \ce{C60} and \ce{C70} fullerenes) does not have a layered structure. Both fullerenes have a cage-like morphology and the chloroaluminates are not small enough to move in and out of them during charge/discharge. We suggest that \ce{AlCl4-} anions migrated through the gaps present in between the fullerenes without altering its molecular structure. Using a \textit{Neware BTS 3000} battery analyser, specific capacities of the cathodes were recorded at a constant current density of 50 mA g$^{-1}$ (cf.\ Figure \ref{fig:CDCall}a and b). Morphology of the cathodes before and after the cycles were studied using Raman spectroscopy, X-ray diffraction (XRD) patterns and scanning electron microscopy (SEM).

Figure \ref{fig:CDCall}a and b compares the specific capacities of all cells for their first and 50$^{th}$ cycles. Human hair cathodes exhibited a high capacity of $\sim$100 mAh g$^{-1}$ with coulombic efficiency of $\sim$95$\%$. High surface area due to its porous structure might have led to an additional 'capacitor-like' charge storage \cite{frackowiak_carbon_2001}. Hemp batteries displayed a capacity of 56 mAh g$^{-1}$ in their first cycle, which decreased to 45 mAh g$^{-1}$ after 50 cycles. CFEx displayed a capacity of around 80 mAh g$^{-1}$ with coulombic efficiency of $\sim$90\%. With an initial value of 84 mAh g$^{-1}$, specific capacity of SPCB decreased to 47 mAh g$^{-1}$ with a low coulombic efficiency of $\sim$40\%. Capacity for SPCB and hemp cells decreased considerably after repeated charge/discharge cycles. A low coulombic efficiency (observed in both hemp and SPCB) can be attributed to side reactions in a battery. These may include electrode or electrolyte interactions with impurities, or degradation of the cathode structure (pulverisation) \cite{gyenes_understanding_2015-1}. However, capacity fade for CFEx and human hair cells was minimal. This suggests that CFEx and human hair have a more stable structure and have the potential to store charge reversibly \cite{pramanick_human_2016}.

% In the above paragraph, you discuss 3 specific cells. This is suicidal (metaphorically speaking). In science you make a point by showing that something is reproducible. Having done just 3 expriments is asking for the reviewer to knock it down. You need to re-write this in a more general manner.
\fbox{\begin{minipage}{46.5em}
\section*{Activation of carbon}
The production of activated carbon consists of carbonisation of a precursor at a temperature below 900$^{\circ}$ C in an inert atmosphere and chemical or physical activation of the carbonised precursor. Activating agents play an important role in determining the porosity of an activated carbon \cite{arenas_effect_2004}. Using alkali hydroxides at high temperature creates micropores which increases the surface area of the material \cite{dong_commercial_2019, liu_hair-based_2017}. In this work, sodium hydroxide (NaOH) was used as the activating agent. The reaction that takes place inside the carbon matrix after adding NaOH is as follows:

\begin{center}
    4NaOH + C $\longrightarrow$ 4Na + 4\ce{CO2} + 2\ce{H2O} \cite{satish_macroporous_2015}
\end{center}

In this reaction, NaOH was reduced to free metal, Na. These atoms in turn expanded the carbon matrix after intercalating into the carbon structure. Increased temperature (750$^{\circ}$ C) forced the  atoms out of the carbon matrix, thus creating micropores. Oxidation of carbon from oxygen atoms of the hydroxide group formed carbon dioxide (\ce{CO2}), providing routes for channeling the sodium atoms into the internal structure, resulting in a well-connected porous structure \cite{satish_macroporous_2015}. The calcinating temperature used here was 750$^{\circ}$ C. Figure \ref{fig:ACHsyn} displays a flowchart describing activated carbon synthesis. 
\end{minipage}}

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{fig/ACHsyn}
\caption{Synthesis of activated carbon (AC) from human hair using NaOH as the activating agent.}
\label{fig:ACHsyn}
\end{figure}

@@

% Above paragraph: Lots of unnecerssary information (see comments). Focus on what is relevant. Also sentences like the Carbon Valley one are suicidal. When you write, always have your worst scientific enemy in mind and write it so that you win.
\begin{figure}[h!]
\centering
\includegraphics[width=0.75\textwidth]{fig/CFExsol}
\caption{Comparison of solubility of a) pure \ce{C60} fullerene b) fullerene extract (CFEx) and AC derived from hemp fibers in \ce{AlCl3}/EMImCl ionic liquid electrolyte.}
\label{fig:CFExsol}
\end{figure}

Fullerenes have a fused-ring structure with a nucleus-to-nucleus diameter of 7.1\AA\ and a van der Waals (vdW) diameter of 11\AA\ in a single crystal. However, they are zero-dimensional materials, which means they cannot provide an efficient path for electron transport or a long-range conductivity \cite{loutfy_fullerene_2002, winkler_two-component_2007}. They are known to be weak battery materials owing to their solubility in electrolytes, especially in LIBs \cite{seger_prospects_1991}. To test their solubility in \ce{AlCl3}-EMImCl, 100 mg of CFEx was mixed in the electrolyte and stirred for 24 hours. The solution was left to stand for another 24 hours inside a \ce{N2}-filled glove box. CFEx seemed to dissolve in the RTIL (Figure \ref{fig:CFExsol}) since no phase separation was observed. It has been reported that poly-sulphides (formed during charge/discharge cycles) are soluble in the electrolyte of a Li-S battery. They form an insulating layer of \ce{Li2S} on the anode, which results in capacity fading \cite{sun_effect_2017}. Since no such effect was observed in aluminium-fullerene cells, the solubility of fullerenes does not seem to impact the charge-storing capacity of CFEx. On the contrary, aluminium-fullerene batteries demonstrated excellent capacity retention at various current rates(Figure \ref{fig:CDCall}d).

 \begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{fig/superPmech}
    \caption{Suggested mechanism for an aluminium-SPCB cell. \ce{AlCl4-} anions intercalate into the very few graphitic planes in Super-P, while few anions adsorb onto its surface. However, further cycling leads to cathode pulverisation, which results in capacity fading.}
  \label{fig:superPmech}
\end{figure}

Super-P is an amorphous form of carbon with a high surface area of 62 m$^2$ g$^{-1}$ and a highly disordered structure. The pore sizes range from $\sim$30-50 nm \cite{younesi_analysis_2015}. As a cathode material, SPCB underwent the highest capacity loss within 30 cycles (45\%). It seems continuous cycling destroyed the structural arrangement of the carbon atoms, which resulted in further alleviated capacity and low coulombic efficiencies.

 \begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{fig/hempmech}
    \caption{Suggested mechanism for an aluminum-hemp cell. Hemp fibers have pore sizes which might be as large as 2.0-2.5 $\mu$m allowing the \ce{AlCl4-} to get absorbed on their surface. However, agglomeration of these fibers after a few cycles reduces the number of active sites available for effective charge storage.}
  \label{fig:hempmech}
\end{figure}

 \begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{fig/raman}
    \caption{Raman spectra of pristine (in black) and charged (in red) a) CFEx, b) hemp, c) human hair and d) SPCB cathodes displaying presence of both D and G bands.}
  \label{fig:raman}
\end{figure}

It has been previously established that chloroaluminates intercalate into the graphitic planes during charging \cite{lin_ultrafast_2015-3}. Since activated carbon and SPCB cathodes tested in this work have graphitic planes present in them, we compared the pristine and charged electrodes only. Figure \ref{fig:raman} displays the Raman spectra of the pristine and charged (intercalated) cathodes. Pristine hair, hemp and SPCB cathodes had a significant D-band present in them, indicating absence of an ordered structure (at $\sim$1300 cm$^{-1}$ for human hair, 1329.7 cm$^{-1}$ for hemp fibers, and 1352.0 cm$^{-1}$ for SPCB). Broad peaks at about 1600 cm$^{-1}$ and about 1350 cm$^{-1}$ arise from \ce{sp2} clusters like $\alpha$-carbons with bond angle disorder \cite{shimo}. Raman spectra of CFEx in Figure \ref{fig:raman}c displayed the characteristic features of both \ce{C60} and \ce{C70} molecules. A 'pentagonal pinch mode', usually observed in a \ce{C60} Raman spectrum, was present at 1460 cm$^{-1}$. \ce{C70} has multiple bands because it has a reduced molecular symmetry, which increases the number of vibrational modes, consequently increasing the number of active Raman bands \cite{kimbrell_analysis_2014}. It was interesting to note that the spectra of charged CFEx looked strikingly similar to the pristine ones, Figure \ref{fig:raman}c. Since Raman spectroscopy is sensitive to minute differences in the molecular morphology, results suggested that the fullerenes did not undergo any significant structural change during cycles. Charged AC (from hair) cathodes showed an increased full-width at half maxima (FWHM), which suggested an increase in the lattice defects and structure deformities. Obviously, these defects arise after intercalation of chloroaluminates into the few graphitic planes present in the carbon matrix. Furthermore, a highly porous structure allows surface adsorption of charge carrying species (much like in super-capacitors) \cite{beguin_carbons_2014}. Intercalation into graphitic planes/micropores, along with surface adsorption of chloroaluminates, result in aluminium-hair batteries performing better than other materials by storing more charge \cite{brezesinski_ordered_2010}. Schematic of an aluminium-hair battery is illustrated in Figure \ref{fig:ACHmech}.

 \begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{fig/ACHmech}
    \caption{Suggested mechanism for an aluminium-human hair cell. Chloroaluminates (\ce{AlCl4-}) intercalate into the few graphitic planes and micro/mesopores present in them, in addition to surface adsorption of ions displaying both Faradaic and non-Faradaic processes for charge storage.}
  \label{fig:ACHmech}
\end{figure}

%contains about 51\% carbon, 17\% nitrogen, 21\% oxygen, 6\% hydrogen, 5\% sulfur, and trace amounts of iron, magnesium, arsenic, chromium and various minerals \cite{lee_chemistry}.  
Hemp fibers and SPCB had a highly disordered structure to begin with. Repeated intercalation or absorption of ions on their surface in the first few cycles would have further increased the lattice defects, which is one of the reasons why hemp and SPCB batteries failed to retain their capacity. However, CFEx does not have graphitic planes to intercalate chloroaluminate ions. Since the fullerenes have a very high surface area, surface adsorption of ions is highly likely \cite{adams_van_1994}. Furthermore, it might be possible for the anions to seep through the gaps present in between two fullerenes (as shown in Figure \ref{fig:CFExmech}) and for the surface-based redox processes to take place in a systematic way.
